Hardware-Accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-06-23 paper.tex
Removed sentence about multiple camera angles (ref #17)
Updated numbers in performance table (ref #17)

The performance of each approach was measured by using a simple frame counter
showing the number of frames rendered in the previous second.  Multiple camera
angles and scene configurations were tried in order to expose strong and weak
points of the approaches.  The tests were run on three different machines with a
variety of operating systems (Linux, Mac OS X) and video cards (ATI, NVIDIA).
Table \ref{performance-table} shows the results.

\begin{table}
  \centering
  \begin{tabular}{ l r r r }
    \toprule
    Approach & Macbook & Desktop & Workstation\\
    \midrule
    Boolean AND with masking & 22 & 13 & 51 \\
    Boolean AND with XOR & 24 & 13 & 76 \\
    Slicing & 6 & 18 & 130 \\
    Optimized Slicing & 25 & 15 & 172 \\
    \bottomrule
  \end{tabular}
  \caption{Performance measurements}
  \label{performance-table}
\end{table}

>>>>

The performance of each approach was measured by using a simple frame counter
showing the number of frames rendered in the previous second.  The tests were
run on three different machines with a variety of operating systems (Linux, Mac
OS X) and video cards (ATI, NVIDIA).  Table \ref{performance-table} shows the
results.

\begin{table}
  \centering
  \begin{tabular}{ l r r r }
    \toprule
    Approach & Macbook & Desktop & Workstation\\
    \midrule
    Boolean AND with masking & 12 & 4 & 37 \\
    Boolean AND with XOR & 12 & 4 & 38 \\
    Slicing & 12 & 3 & 32 \\
    Optimized Slicing & 3 & 3 & 35 \\
    \bottomrule
  \end{tabular}
  \caption{Performance measurements}
  \label{performance-table}
\end{table}
